### 2019-05-09 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
I'm happy about the modifications for Chapter 5:
- no proof for lower-bound
- less figures
- shorter Appendix
- few more details in a proof
- less clutter in some equations

% -----------------------------------------------------------------
\section{An improved asymptotic regret lower bound (for some algorithms)}
\label{sec:5:lowerbound}
% -----------------------------------------------------------------

@@

% FIXME
% \begin{framed}
  \textbf{\textcolor{red}{Warning}.}
  The regret lower bound given in \cite{Besson2018ALT} is not applicable to any algorithm,
  as it was discovered by Etienne Boursier and Vianney Perchet, as they explain in Section~2.4 in \cite{BoursierPerchet18}.
  The proof we gave in the Appendix of our paper \cite{Besson2018ALT} was wrong in just one step,
  but the results stated in this section are now correct,
  thanks to the modifications proposed by Emilie Kaufmann and Abbas Mehrabian in Appendix~E of \cite{KaufmannAbbas19}.
  The cost for this modification is to restrict the lower-bound to a smaller class of algorithms, which contains both \RhoRand{} and our two proposals \RandTopM{} and \MCTopM{} but not the two algorithms proposed SIC-MMAB from \cite{BoursierPerchet18} and Multiplayer Explore-then-Commit (M-ETC) from \cite{KaufmannAbbas19}.
% \end{framed}
% FIXME

@@

The regret decomposition in Lemma~\ref{lem:5:DecompositionRegret} is valid for both centralized and decentralized algorithms.
For centralized algorithms, due to the absence of collisions, \ref{eq:5:term3} is obviously zero, and \ref{eq:5:term2} is non-negative, as $T_k(T) \leq T$. For decentralized algorithms, \ref{eq:5:term3} may be significantly large, and term \ref{eq:5:term2} may be negative, as many collisions on arm $k$ may lead to $T_k(T) > T$ (which is counter intuitive with such notations).
However, a careful manipulation of this decomposition shows that the regret is always lower bounded by term \ref{eq:5:term1}.

@@

Similarly to what we present above in Chapter~\ref{chapter:2}, Section~\ref{sec:2:lowerUpperBoundsRegret},
we use the Kullback-Leibler divergence to express our lower bound.
Let $\kl(x,y) := x\log(x/y) + (1-x)\log((1-x)/(1-y))$ be KL divergence between the Bernoulli distribution of mean $x$ and that of mean $y$.
%
We first introduce the assumption under which we derive a regret lower bound, that generalizes a classical assumption made by \cite{LaiRobbins85} in single-player bandit models.
Our lower bound will only be valid for algorithms of a certain class, that do not obtain much information from the collision indicator variables.
This class contains our proposals, \RandTopM{} and \MCTopM, but rules out the \textsc{Sic-MMAB} algorithm of \cite{BoursierPerchet18}.

@@

As it was discovered in \cite{BoursierPerchet18} and further explained in Appendix~E of \cite{KaufmannAbbas19}, our lower-bound was not true for any algorithm, as we wrongly claimed in \cite{Besson2018ALT} that the ``collision information term'' is zero for any algorithm $\rho$.
However, we wanted to be still able to present the derivations of our lower-bound, mainly because its proof and its form give insights on how to design an asymptotically optimal algorithm $\rho$, and because it still applies to algorithms of the \RhoRand{} family as well as our proposals \RandTopM{} and \MCTopM.

@@

Fix a problem $\bm{\mu}$, and as we do in Appendix~\ref{proof:5:BetterLowerBound}, introduce an alternative model parametrized by $\bm{\lambda}$, with a small difference between $\bm{\mu}$.
Fix a sub-optimal arm $k$ and $\varepsilon>0$, and $\lambda_k = \mu^*_M + \varepsilon$ and $\lambda_{\ell} = \mu_{\ell}$ for any $\ell\neq k$.
We denote $\Pr_{\bm{\mu}}^{\cO_t}$ the distribution of the vector $\cO_t$ under the model $\bm{\mu}$ when using algorithm $\rho$.
Then we introduce the \emph{collision information term} as:
\begin{equation}\label{eq:5:collisionInformationTerm}
  \cI_{\bm{\mu},\bm{\lambda}}(\rho,T) := \sum_{t=1}^{T} \mathrm{KL}(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}}, \Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}).
\end{equation}

For a \emph{decentralized strategy} $\rho$ that has access to the sensing information (\ie, ruling out model \modeltrois), and satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\rho,T) = \smallO{\log(T)}$,
we now state a problem-dependent asymptotic lower bound on the number of sub-optimal arms selections.
The additional hypothesis on $\cI_{\bm{\mu},\bm{\lambda}}(\rho,T)$ essentially says that ``the collisions do not bring too much information on the arm means'', as stated in \cite{KaufmannAbbas19}.
The theorem stated below is proved in Appendix~\ref{proof:5:BetterLowerBound}, and it also yields an asymptotic logarithmic lower bound on the regret.

@@

Interestingly, our lower bound is exactly a multiplicative constant factor $M$ away from the lower bound given by \cite{Anantharam87a} for centralized algorithms (which is clearly a simpler setting). This intuitively suggests the number of players $M$ as the (multiplicative) \emph{``price of decentralized learning''}. However, to establish our regret bound, we lower bounded the number of collisions by zero, which may be too optimistic.
%
Indeed, for an algorithm to attain the lower bound \eqref{eq:5:ourLowerBound}, the number of selections of each sub-optimal arm should match the lower bound \eqref{eq:5:LBDraws} \emph{and} term \ref{eq:5:term2} and term \ref{eq:5:term3} in the regret decomposition of Lemma~\ref{lem:5:DecompositionRegret} should be negligible compared to  $\log(T)$.
To the best of our knowledge, no algorithm has been shown to experience only $o(\log(T))$ collisions so far,
for every $M \in \{2,\dots,K\}$ and $\boldsymbol{\mu} \in \cP_M$.
%
Since our article \cite{Besson2018ALT}, we kept as a future work the following question.
A lower bound on the minimal number of collisions experienced by any strongly uniformly efficient decentralized algorithm would thus be a nice complement to our Theorem~\ref{thm:5:BetterLowerBound}.

@@

Given any of these two index policies (\UCB{} or \klUCB), the \Selfish{} algorithm is defined by,
%
\begin{equation}
  A^j(t) = \argmax{ k \in \{1,\dots,K\}} \ \widetilde{g_k}^j(t-1).\label{algo:5:Selfish}
\end{equation}
The name comes from the fact that each player is targeting, in a ``selfish'' way, the arm that has the highest index, instead of accepting to target only one of the $M$ best.
The reason that this may work precisely comes from the fact that $\widetilde{g_k}^j(t)$ is no longer an upper-confidence on $\mu_k$,
but some hybrid index that simultaneously increases when a transmission occurs and decreases when a collision occurs.

@@

We show in Section~\ref{sub:5:SelfishFails} that \Selfish{} does have a (very) small probability to fail (badly), for some problem with small $K$,
which precludes the possibility of a logarithmic regret for any problem.
In most cases, it empirically performs similarly to all the algorithms described before,
and usually outperforms \rhoRand,
even if it neither exploits the sensing information, nor the knowledge of the number of players $M$.
%
Practitioners may still be interested by the algorithm, especially for Cognitive Radio applications in which sensing is hard or cannot be considered.
Thus we propose next our main contribution, the \MCTopM{} algorithm, proved to be asymptotically optimal for the identification of suboptimal arms (when using \klUCB), attaining order-optimal logarithmic regret, and outperforming all the other algorithms for the ``sensing case''.

@@

@@

\paragraph{The \RandTopM{} algorithm.}
%
First, we precisely state the \RandTopM{} algorithm above in Algorithm~\ref{algo:5:RandTopM}.
It is essentially a refinement over the \RhoRand{} algorithm, to not use the indirection of ranks, and a simpler version of \MCTopM.
The difference with \MCTopM{} is that the later algorithm introduces a concept of a ``Chair'', by considering a binary ``being fixed'' state $s^j(t)$, as presented in Algorithm~\ref{algo:5:MCTopM} below.
%
In \RandTopM{}, player $j$ is always considered ``not fixed'',
and a \emph{collision always forces a uniform sampling of the next arm} from $\TopM(t)$.

@@

\begin{figure}[h!]
  \resizebox{1.00\textwidth}{!}{
  \begin{tikzpicture}[>=latex',line join=bevel,scale=5.5]
      %
      \node (start) at (1.5,0.30) {$(0)$ Start $t=0$};
      \node (notfixed) at (1,0) [draw,rectangle,thick] {Not fixed, $\overline{s^j(t)}$};
      \node (fixed) at (0,0) [draw,rectangle,thick] {Fixed, $s^j(t)$};
      %
      \draw [black,->] (start) -> (notfixed.20);
      \draw [color=cyan,thick,->] (notfixed) to[bend right] node[midway,above,text width=5cm,text centered,black] {\small $(1)$ $\overline{C^j(t)}, A^j(t) \in \TopM(t)$} (fixed);
      \path [color=blue,thick,->] (notfixed) edge[loop right] node[right,text width=4cm,text badly centered,black] {\small $(2)$  $C^j(t), A^j(t) \in \TopM(t)$} (1);
      \path [color=red,thick,->] (notfixed) edge[loop below] node[below,text centered,black] {\small $(3)$  $A^j(t) \notin \TopM(t)$} (1);
      \path [color=darkgreen,thick,->] (fixed) edge[loop left] node[left,text width=2.9cm,text badly centered,black] {\small $(4)$ $A^j(t) \in \TopM(t)$} (fixed);
      \draw [color=red,thick,->] (fixed) to[bend right] node[midway,below,text centered,black] {\small $(5)$  $A^j(t) \notin \TopM(t)$} (notfixed);
      %
  \end{tikzpicture}
  }
  \caption[``State-machine'' representation of \MCTopM]{Player $j$ using \MCTopM, represented as ``state machine'' with $5$ transitions.
  Taking one of the five transitions means playing one round of the Algorithm~\ref{algo:5:MCTopM}, to decide $A^j(t+1)$ using information of previous steps.}
  \label{fig:5:StateMachineAlgorithm_MCTopM}
\end{figure}

@@

  Thanks to \eqref{eq:5:KeyInclusion} and if $\Pr_{\bm{\mu}} $ denote here the probability under model $\bm{\mu}$, it is easy to decompose the number of selections of arm $k$ by user $j$ up to round $T$ as
  \begin{align*}
  \E_{\mu}[T_k^j(T)]
  &= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
  = \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k \right).\\
  %&= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\Mbest,\; g_m(t) < g_k(t) \right) \\
  &= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}^j(t) < g_k^j(t) \right).
  %
  \end{align*}
  Considering the relative position of the upper-confidence bound $g_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition
  \begin{align*}
    \E_{\mu}[T_k^j(T)] &\leq \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}(t) \leq g_k(t) , \forall m \in \{1,\dots,M\}: \;  g_{m^*}(t) \geq \mu_m^* \right)\\
    &\;\;\;\;\;\;\;\; + \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m \in\{1,\dots,M\}: \; g_{m^*}(t) < \mu_m^* \right) \\
    &\leq \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; \mu_{m}^* \leq g_k(t)\right)+ \sum_{m=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(g_{m^*}(t) < \mu_m^* \right) \\
    %
    & \leq \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq g_k(t) \right)
    + \sum_{m=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( g_{m^*}(t) < \mu_m^* \right)
    \hspace*{80pt} (\heartsuit)  % TODO cleaner?
  \end{align*}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in \{1, \dots,M\}$.

  Now each of the two terms in the right hand side of $(\heartsuit)$ can directly be upper bounded using tools developed by \cite{KLUCBJournal} for the analysis of kl-UCB.
  The rightmost term in $(\heartsuit)$ can be controlled using Lemma~\ref{lem:5:Fact1KLUCB} below that relies on a self-normalized deviation inequality, whose proof exactly follows from the proof of Fact~1 in Appendix~A of \cite{KLUCBJournal}.

@@

  The leftmost term in $(\heartsuit)$ can be controlled using Lemma~\ref{lem:5:Fact2KLUCB}, that is a direct consequence of the proof of Fact~2 in Appendix~A of \cite{KLUCBJournal}.
  Denote $\kl'(x,y)$ the derivative of the function $x \mapsto \kl(x,y)$ (for any fixed $y\neq 0, 1$).

>>>>

% -----------------------------------------------------------------
% \section{An improved asymptotic regret lower bound (for some algorithms)}
\section{Decomposing the regret to get an intuition for the design of efficient decentralized algorithms}
\label{sec:5:lowerbound}
% -----------------------------------------------------------------

@@

% FIXME
% \begin{framed}
  \textbf{\textcolor{red}{Warning}.}
  The regret lower bound given in \cite{Besson2018ALT} is not applicable to any algorithm,
  as it was discovered by Etienne Boursier and Vianney Perchet, as they explain in Section~2.4 in \cite{BoursierPerchet18}.
  The proof we gave in the Appendix of our paper \cite{Besson2018ALT} was wrong in just one step,
  but the results stated in this section are now correct,
  thanks to the modifications proposed by Emilie Kaufmann and Abbas Mehrabian in Appendix~E of \cite{KaufmannAbbas19}.
  The cost for this modification is to restrict the lower-bound to a smaller class of algorithms, which \emph{should} contain \RhoRand, \RandTopM{} and \MCTopM, but not the two algorithms proposed SIC-MMAB from \cite{BoursierPerchet18} and Multiplayer Explore-then-Commit (M-ETC) from \cite{KaufmannAbbas19}.
  Proving that the proposed algorithms are in this class is left as an open question.
% \end{framed}
% FIXME

@@

The regret decomposition in Lemma~\ref{lem:5:DecompositionRegret} is valid for both centralized and decentralized algorithms.
For centralized algorithms, due to the absence of collisions, \ref{eq:5:term3} is obviously zero, and \ref{eq:5:term2} is non-negative, as $T_k(T) \leq T$. For decentralized algorithms, \ref{eq:5:term3} may be significantly large, and term \ref{eq:5:term2} may be negative, as many collisions on arm $k$ may lead to $T_k(T) > T$ (which is counter intuitive with such notations).
However, a careful manipulation of this decomposition shows that the regret is always lower bounded by term \ref{eq:5:term1}.
The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} in Appendix illustrate two cases of $M<K$ and $M=K$ and the different impact of the three terms (\ref{eq:5:term1}, \ref{eq:5:term2} and \ref{eq:5:term3}) on the regret.

@@

Similarly to what we present above in Chapter~\ref{chapter:2}, Section~\ref{sec:2:lowerUpperBoundsRegret},
we use the Kullback-Leibler divergence to express our lower bound.
Let $\kl(x,y) := x\log(x/y) + (1-x)\log((1-x)/(1-y))$ be KL divergence between the Bernoulli distribution of mean $x$ and that of mean $y$.
%
We first introduce the assumption under which we derive a regret lower bound, that generalizes a classical assumption made by \cite{LaiRobbins85} in single-player bandit models.
% Our lower bound will only be valid for algorithms of a certain class, that do not obtain much information from the collision indicator variables.
% This class contains our proposals, \RandTopM{} and \MCTopM, but rules out the \textsc{Sic-MMAB} algorithm of \cite{BoursierPerchet18}.

@@

As it was discovered in \cite{BoursierPerchet18} and further explained in Appendix~E of \cite{KaufmannAbbas19}, our lower-bound was not true for any algorithm, as we wrongly claimed in \cite{Besson2018ALT} that the ``collision information term'' is zero for any algorithm $\rho$.
However, we wanted to be still able to present the derivations of our lower-bound, mainly because its proof and its form give important insights on how to design an asymptotically optimal algorithm $\rho$.
% and because it still applies to algorithms of the \RhoRand{} family as well as our proposals \RandTopM{} and \MCTopM.

@@

Fix a problem $\bm{\mu}$,
% and as we do in Appendix~\ref{proof:5:BetterLowerBound},
then introduce an alternative model parametrized by $\bm{\lambda}$, with a small difference between $\bm{\mu}$.
Fix a sub-optimal arm $k$ and $\varepsilon>0$, and $\lambda_k = \mu^*_M + \varepsilon$ and $\lambda_{\ell} = \mu_{\ell}$ for any $\ell\neq k$.
We denote $\Pr_{\bm{\mu}}^{\cO_t}$ the distribution of the vector $\cO_t$ under the model $\bm{\mu}$ when using algorithm $\rho$.
Then we introduce the \emph{collision information term} as:
\begin{equation}\label{eq:5:collisionInformationTerm}
  \cI_{\bm{\mu},\bm{\lambda}}(\rho,T) := \sum_{t=1}^{T} \mathrm{KL}(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}}, \Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}).
\end{equation}

For a \emph{decentralized strategy} $\rho$ that has access to the sensing information (\ie, ruling out model \modeltrois), and satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\rho,T) = \smallO{\log(T)}$,
we now state a problem-dependent asymptotic lower bound on the number of sub-optimal arms selections.
The additional hypothesis on $\cI_{\bm{\mu},\bm{\lambda}}(\rho,T)$ essentially says that ``the collisions do not bring too much information on the arm means'', as stated in \cite{KaufmannAbbas19}.
The theorem stated below is proved in the Appendix of \cite{Besson2018ALT},
% \ref{proof:5:BetterLowerBound},
and it also yields an asymptotic logarithmic lower bound on the regret.

@@

\paragraph{Price of decentralized learning?}
%
Interestingly, our lower bound is exactly a multiplicative constant factor $M$ away from the lower bound given by \cite{Anantharam87a} for centralized algorithms (which is clearly a simpler setting). This intuitively suggests the number of players $M$ as the (multiplicative) \emph{``price of decentralized learning''}. However, to establish our regret bound, we lower bounded the number of collisions by zero, which may be too optimistic.
%
Indeed, for an algorithm to attain the lower bound \eqref{eq:5:ourLowerBound}, the number of selections of each sub-optimal arm should match the lower bound \eqref{eq:5:LBDraws} \emph{and} term \ref{eq:5:term2} and term \ref{eq:5:term3} in the regret decomposition of Lemma~\ref{lem:5:DecompositionRegret} should be negligible compared to  $\log(T)$.
To the best of our knowledge, no algorithm has been shown to experience only $o(\log(T))$ collisions so far,
for every $M \in \{2,\dots,K\}$ and $\boldsymbol{\mu} \in \cP_M$.
%
Since our article \cite{Besson2018ALT}, we kept as a future work the following question.
A lower bound on the minimal number of collisions experienced by any strongly uniformly efficient decentralized algorithm would thus be a nice complement to our Theorem~\ref{thm:5:BetterLowerBound}.

@@

Given any of these two index policies (\UCB{} or \klUCB), the \Selfish{} algorithm is defined by,
%
\begin{equation}
  A^j(t) = \argmax_{ k \in \{1,\dots,K\}} \ \widetilde{g_k}^j(t-1).\label{algo:5:Selfish}
\end{equation}
The name comes from the fact that each player is targeting, in a ``selfish'' way, the arm that has the highest index, instead of accepting to target only one of the $M$ best.
The reason that this may work precisely comes from the fact that $\widetilde{g_k}^j(t)$ is no longer an upper-confidence on $\mu_k$,
but some hybrid index that simultaneously increases when a transmission occurs and decreases when a collision occurs.

@@

We illustrate in Section~\ref{sub:5:SelfishFails} that \Selfish{} does have a (very) small probability to fail (badly), for some problem with small $K$,
which precludes the possibility of a logarithmic regret for any problem.
In most cases, it empirically performs similarly to all the algorithms described before,
and usually outperforms \rhoRand,
even if it neither exploits the sensing information, nor the knowledge of the number of players $M$.
%
Practitioners may still be interested by the algorithm, especially for Cognitive Radio applications in which sensing is hard or cannot be considered.
Thus we propose next our main contribution, the \MCTopM{} algorithm, proved to be asymptotically optimal for the identification of suboptimal arms (when using \klUCB), attaining order-optimal logarithmic regret, and outperforming all the other algorithms for the ``sensing case''.

@@

\paragraph{The \RandTopM{} algorithm.}
%
We precisely state our first proposal below in Algorithm~\ref{algo:5:RandTopM}.

@@

\RandTopM{} is essentially a refinement over \RhoRand, to not use the indirection of ranks, and a simpler version of \MCTopM.
The difference with \MCTopM{} is that the later introduces a concept of a ``Chair'', by considering a binary ``being fixed'' state $s^j(t)$, as presented in Algorithm~\ref{algo:5:MCTopM} below.
%
In \RandTopM{}, player $j$ is always considered ``not fixed'',
and a \emph{collision always forces a uniform sampling of the next arm} from $\TopM(t)$.

@@

\begin{figure}[h!]
  \resizebox{1.00\textwidth}{!}{
  \begin{tikzpicture}[>=latex',line join=bevel,scale=5.8]
      %
      \node (start) at (1.5,0.30) {$(0)$ Start $t=0$};
      \node (notfixed) at (1,0) [draw,rectangle,thick] {Not fixed, $\overline{s^j(t)}$};
      \node (fixed) at (0,0) [draw,rectangle,thick] {Fixed, $s^j(t)$};
      %
      \draw [black,->] (start) -> (notfixed.20);
      \draw [color=cyan,thick,->] (notfixed) to[bend right] node[midway,above,text width=5cm,text centered,black] {\small $(1)$ $\overline{C^j(t)}, A^j(t) \in \TopM(t)$} (fixed);
      \path [color=blue,thick,->] (notfixed) edge[loop right] node[right,text width=4cm,text badly centered,black] {\small $(2)$  $C^j(t), A^j(t) \in \TopM(t)$} (1);
      \path [color=red,thick,->] (notfixed) edge[loop below] node[below,text centered,black] {\small $(3)$  $A^j(t) \notin \TopM(t)$} (1);
      \path [color=darkgreen,thick,->] (fixed) edge[loop left] node[left,text width=2.9cm,text badly centered,black] {\small $(4)$ $A^j(t) \in \TopM(t)$} (fixed);
      \draw [color=red,thick,->] (fixed) to[bend right] node[midway,below,text centered,black] {\small $(5)$  $A^j(t) \notin \TopM(t)$} (notfixed);
      %
  \end{tikzpicture}
  }
  \caption[``State-machine'' representation of \MCTopM]{Player $j$ using \MCTopM, represented as ``state machine'' with $5$ transitions.
  Taking one of the five transitions means playing one round of the Algorithm~\ref{algo:5:MCTopM}, to decide $A^j(t+1)$ using information of previous steps.}
  \label{fig:5:StateMachineAlgorithm_MCTopM}
\end{figure}

@@

  Thanks to \eqref{eq:5:KeyInclusion} and if $\Pr_{\bm{\mu}} $ denote here the probability under model $\bm{\mu}$, it is easy to decompose the number of selections of arm $k$ by user $j$ up to round $T$ as
  \begin{align*}
  \E_{\mu}[T_k^j(T)]
  &= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
  = \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k \right).\\
  %&= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\Mbest,\; g_m(t) < g_k(t) \right) \\
  &= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\{1,\dots,M\}:\; g_{m^*}^j(t) < g_k^j(t) \right).
  %
  \end{align*}
  Considering the relative position of the upper-confidence bound $g_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition
  \begin{align}
    \E_{\mu}[T_k^j(T)] &\leq
    \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m_1 \in \{1,\dots,M\}: \; g_{m_1^*}(t) < \mu_m^* \right) + \notag \\
    \;\;\;\;
    \sum_{t=1}^T\Pr_{\bm{\mu}} & \left(A^j(t) = k,\;\; \exists m_2 \in \{1,\dots,M\}:\; g_{m_2^*}(t) \leq g_k(t) , \forall {m_3} \in \{1,\dots,M\}: \;  g_{{m_3}^*}(t) \geq \mu_{m_3}^* \right) \notag \\
    &\leq \sum_{m_1=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(g_{m_1^*}(t) < \mu_{m_1}^* \right) + \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m_2 \in \{1,\dots,M\}:\; \mu_{m_2}^* \leq g_k(t)\right) \notag \\
    %
    & \leq \sum_{m_1=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( g_{m_1^*}(t) < \mu_{m_1}^* \right)
    + \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq g_k(t) \right)
    \label{eq:5:sumOfProbaForTkj}
  \end{align}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in \{1, \dots,M\}$.

  Now each of the two terms in the right hand side of \eqref{eq:5:sumOfProbaForTkj} can directly be upper bounded using tools developed by \cite{KLUCBJournal} for the analysis of kl-UCB.
  The leftmost term in \eqref{eq:5:sumOfProbaForTkj} can be controlled using Lemma~\ref{lem:5:Fact1KLUCB} below that relies on a self-normalized deviation inequality, whose proof exactly follows from the proof of Fact~1 in Appendix~A of \cite{KLUCBJournal}.

@@

  The rightmost term in \eqref{eq:5:sumOfProbaForTkj} can be controlled using Lemma~\ref{lem:5:Fact2KLUCB}, that is a direct consequence of the proof of Fact~2 in Appendix~A of \cite{KLUCBJournal}.
  Denote $\kl'(x,y)$ the derivative of the function $x \mapsto \kl(x,y)$ (for any fixed $y\neq 0, 1$).
